---
title: "Eligibility Tracker"
reference-location: margin
citation-location: margin
editor_options: 
  chunk_output_type: console
comments:
  hypothesis:
    theme: clean
---

```{r}
library(dplyr)

dttm <- Sys.time() |> 
  .POSIXct("MST") |> 
  format("%Y-%m-%d %H:%M %Z")

today <- Sys.time() |> .POSIXct("MST") |> lubridate::as_date()

meta <- read.csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vThN94KzaEV4gk9lICkn7HnOJTAPtTDQuDypir_pxXMzwi7oGxgBbM21gVx6vjHoz-KZV2Jl0kHIhvm/pub?gid=1566653249&single=true&output=csv"
) |> 
  janitor::clean_names() |> 
  mutate(
    across(
      c(start, end),
      ~ lubridate::ymd(.x)
    )
  )
```


Last updated on `r dttm`.

___

# Starlets: SFVRD

```{r}
days2go <- (meta[11,]$end - today) |> 
  as.numeric("days")
```

> Eligibility closes in `r days2go` days.

Check eligibility [here](eligibility_sfvrd.html)

Eligibility criteria:

```{r}
meta |> 
  slice(11) |> 
  select(
    - game
  ) |> 
  kableExtra::kable(
    table.attr = 'data-quarto-disable-processing="true"'
  ) %>% 
  kableExtra::kable_styling(
    bootstrap_options = c("basic", "hover"), 
    full_width = FALSE
  )
```

___

# Starlets: Tucson

```{r}
days2go <- (meta[14,]$end - today) |> 
  as.numeric("days")
```

> Eligibility closes in `r days2go` days.

Check eligibility [here](eligibility_smashers.html)

Eligibility criteria:

```{r}
meta |> 
  slice(14) |> 
  select(
    - game
  ) |> 
  kableExtra::kable(
    table.attr = 'data-quarto-disable-processing="true"'
  ) %>% 
  kableExtra::kable_styling(
    bootstrap_options = c("basic", "hover"), 
    full_width = FALSE
  )
```

___


# Starlets: Calgary

```{r}
days2go <- (meta[13,]$end - today) |> 
  as.numeric("days")
```

> Eligibility closes in `r days2go` days.

Check eligibility [here](eligibility_smashers.html)

Eligibility criteria:

```{r}
meta |> 
  slice(13) |> 
  select(
    - game
  ) |> 
  kableExtra::kable(
    table.attr = 'data-quarto-disable-processing="true"'
  ) %>% 
  kableExtra::kable_styling(
    bootstrap_options = c("basic", "hover"), 
    full_width = FALSE
  )
```

___
